%-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,12pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontspec}
\setmainfont{Arial}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1cm, top=0.5cm, right=1cm, bottom=0.5cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-1.0mm}\item[]
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-1.0mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item[]
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\bullet$}
% \renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{justify}\begin{itemize}[leftmargin=*,itemsep=0.5mm,noitemsep,labelsep=1.2mm, rightmargin=2ex]\small}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0.8mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Harsh Khandelwal} % Your Name
\newcommand{\phone}{9664491854} % Your Phone Number
\newcommand{\emaila}{harsh32.hk@gmail.com} %Email 1

\begin{document}
%\fontfamily{phv}\selectfont
%----------HEADING-----------------

\parbox{\dimexpr\linewidth-0.5cm\relax}{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name}\\
  {Software Engineer} & \raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila} \\
  \href{https://www.linkedin.com/in/harsh-khandelwal-094866201/}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ LinkedIn - Harsh Khandelwal} &  {\raisebox{0.0\height}{\footnotesize \faPhone}\ +91-\phone} \\
  \href{https://github.com/redhlk}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub - \name}}
  & {\raisebox{0.0\height}{\footnotesize}\ Jaipur, Rajasthan, India}\\
\end{tabularx}
}

%-----------PROFESSIONAL SUMMARY-----------
\section{\textbf{Professional Summary}}
\begin{justify}
  Software Engineer with 2+ years of experience in backend development, proficient in Java, Python, and C++ with focus in optimizing performance, debugging, and enhancing system efficiency, contributing to improved customer satisfaction. Experienced in Agile methodologies and pledged to continuous learning.
\end{justify}
%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology, Warangal (NIT Warangal)}{CGPA: 8.3}
      {Master of Science - Mathematics and Computer Science}{Aug. 2020 -  Jun. 2022}
    \resumeSubheading
      {The ICFAI University, Jaipur}{CGPA: 9.28}
      {Bachelor of Science - Mathematics}{Aug. 2017 - Jun. 2020}
  \resumeSubHeadingListEnd
\vspace{-13pt}

%-----------TECHNICAL SKILLS-----------
\section{\textbf{Skills}}
\resumeHeadingSkillStart
    \item \textbf{Languages}{: Java, Python, C++, C     }
    \item \textbf{Frameworks}{: Dropwizard, Express.js, React.js, Node.js          }
    \item \textbf{Tools \& Technologies}{: SQL, Git, Terraform, Oracle Cloud ,Linux         }
    \item \textbf{Areas of Expertise}{: Backend Development, Data Structures, Algorithms, Object-Oriented Programming (OOP), Agile Methodologies                   }
\resumeHeadingSkillEnd
\vspace{4pt}

%-----------EXPERIENCE-----------
\section{\textbf{Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oracle}{India}
      {MTS}{Jul. 2022 - Present}
      \resumeItemListStart
        \item {Collaborated with a global team of 30+ members to develop the Operating System Management Service (OSMS).}
        \item {Developed a Python-based CLI tool for OSMS v1 to v2 migration using Oracle Cloud Infrastructure and Python SDK enabling over 1000 companies/customers to reduce there migration time up to 90\%. Spearheaded the end-to-end infrastructure and application migration tool release, orchestrating a seamless transition that enhanced deployment efficiency.    }
        \item {Enhanced existing system efficiency by 20\% through refactoring and optimization of key processes.}
        \item {Facilitated in code reviews and provided constructive feedback, leading to a 15\% reduction in bugs.}
        \item {Refined cleanup processes for OSMS, reducing inactive users by approximately 50\% in one region and savings substantial resource.}
        \item {Mocked microservices architecture that streamlined local testing processes, resulting in a time savings of 70-80\%; this optimization accelerated the overall development cycle and facilitated quicker deployment of new features.}
        \item {Engineered a Python-based automation tool that created tailored test scenarios for the Migration CLI tool, enhancing the reliability of migration processes while decreasing setup efforts by a notable 50\%.}
        \item {Facilitated seamless onboarding for new team members by creating comprehensive training materials and conducting live demonstrations; this initiative reduced the onboarding process duration by 30\% and improved new hire productivity.}
        \item {Completed over 80 days of On-call shifts, included Migrated database connection pools from c3p0 to HikariCP for multiple services, created Terraform alarms for high-traffic scenarios, and developed business KPIs to track customer activity.}
        \resumeItemListEnd

    % \resumeSubheading
    % \item {Collaborated with a global team of 30+ members to develop the Operating system management service (OSMS).}
    % \item {Developed a Python-based CLI tool for OSMS v1 to v2 migration, including instance creation script and policy-checker for a user , enabling over 1,000 companies to efficiently upgrade and manage their systems.}
    % \item {Reduced up to 20\% on-call bugs by developing the Rest Apis in Modules service, hence making the Spacewalk Microservice aware of the upgradeable module streams.}
    % \item {Completed over 80 days of On-call shifts, included Migrated database connection pools from c3p0 to HikariCP for multiple services,designed interface based mocks for external Api calls, standardized service health metrics, created Terraform alarms for high-traffic scenarios, and developed business KPIs to track customer activity.}
    % \item {Improved cleanup processes for OSMS, reducing inactive users by approximately 50\% in one region and savings substantial resource.}
    %   {JP Morgan Chase \& Co.}{India}
    %   {Software Engineer Intern}{Feb. 2022 - Jun. 2022}
    %   \resumeItemListStart
    %     \item {Worked on asset management applications and performed REST API integrations using Java and Spring Boot.}
    %     \item {Conducted rigorous testing and debugging to ensure high performance and reliability of applications.}
    %     \item {Collaborated with senior developers to implement new features and improve existing functionalities.}
    %   \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-13pt}

%-----------PROJECTS-----------
\section{\textbf{Projects}}
\resumeSubHeadingListStart

    \resumeProject
      {Crypto CLI Tool}
    {}
      {} %Event Dates

      \resumeItemListStart
      \item {Designed and implemented a command-line interface using Python and Typer for a user-friendly experience.}
    \item {Integrated features such as encryption and decryption using Caesar Cipher, RSA, and Vigenere Cipher.}
    \resumeItemListEnd
    \vspace{-2mm}
    
      
  \resumeSubHeadingListEnd
\vspace{-5.5mm}


%-----------EXTRA-CURRICULAR ACTIVITIES-----------
\section{\textbf{Extra-Curricular And Achievement}}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Volunteered}{The ICFAI University, Jaipur}
  {}{Jun. 2020 - Jul. 2020}

      \resumeItemListStart
        % \item {Taught basic computer skills and mathematics to underprivileged children.}
        \item {Crafted and executed 10 innovative teaching modules focused on real-world applications of subject matter; increased student comprehension rates by 25\% as evidenced by pre- and post-module assessments.}
      \resumeItemListEnd


      \resumeSubheading
      {Achievement}{}
      {}{}
      \resumeItemListStart
        \item {Achieved gold medal distinction by ranking first among 50+ students in B.Sc. Mathematics, demonstrating exceptional understanding and application of complex mathematical concepts and theories.}
        \item {Earned a top 1\% rank in the TIFR Mathematics Entrance Exam, competing against 5,000 candidates; this achievement reflects a strong foundation in mathematics and readiness for advanced studies in the field.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-13pt}

\end{document}
